---
title: "multilink"
output: html_document
date: "2024-03-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()
library(janitor)
library(multilink)
library(readr)
library(stringr)
```

## Compare with multilink

We modify one of the Sadinle simulation files, introducing duplications in both datasets. 

```{r}
i = 1
all_patterns <- F
S = 100 # Small S just to make things run faster 
burn = S * .1
m_prior <- u_prior <- alpha <- beta <- 1
files <- list.files(path = "../data/sadinle_sim_data/", full.names = T)

overlap <- 100

records <- read_csv(files[i], col_types = cols())
records$file <- rep(2:1, length.out = dim(records)[1])

records <- records %>%
  janitor::clean_names() %>%
  mutate(rec_id = as.numeric(str_extract(rec_id, "\\d{3}")) + 1)

n1 <- 500
n2 <- 500
#overlap <- n2/2

# Ztrue <- n1 + 1:n2
# Ztrue[1:overlap] <- 1:overlap

# Ztrue <- rep(0, n2)
# Ztrue[1:overlap] <- 1:overlap

file1 <- records %>%
  filter(file ==1,
         rec_id <= n1) %>%
  as.matrix(.) %>%
  data.frame(.) %>%
  mutate(occup = as.numeric(occup))

file2 <- records %>%
  filter(file == 2,
         rec_id %in% c(1:overlap, (n1 +1):(1000 - overlap))) %>%
  as.matrix() %>%
  data.frame(.) %>%
  mutate(occup = as.numeric(occup))

copy_index <- 1:overlap
paste_index <- (overlap +1):(2*overlap)

file1[paste_index, ] <- file1[copy_index, ]
file1 <- file1 %>% 
  arrange(rec_id) %>% 
  select(-rec_id)

file2[paste_index, ] <- file2[copy_index, ]
file2 <- file2 %>% 
  arrange(rec_id) %>% 
  select(-rec_id)

cd <- compare_records(file1, file2, c(2, 3, 5, 6),
                        types = c("lv", "lv", "bi", "bi"))

hash <- hash_comparisons(cd, all_patterns, algorithm = c("vabl", "fabl", "brl"))
```

# Standard fabl

If there are multiple matches in the target file ($X_1$) for a single record in the base file ($X_2)$, fabl will struggle to find matches. In the best case scenario, the one record will have posterior probability 0.51, and the other will have 0.49, and the algorithm will randomly declare one a match through the Bayes estimate. If there are more than two matches, then the probability will likely be too dispersed for the Bayes estimate to identify any as matches. 

```{r}
out <- fabl(hash, S = S, burn = burn)
result <- estimate_links(out, hash, resolve = F)
result$Z_hat

```

# Multiple Match Approach

In this setting, the multiple match approach seems to work well. 

```{r}
out_mm <- fabl_mm_2(hash, S = S, burn = burn)
result_mm <- estimate_links_mm(out_mm, hash, resolve = F)
result_mm$Z_hat

```


# FastLink

At least in this example, standard Fellegi Sunter (as implemented in fastlink) tends to produce false positives. Note that we should not use the Jaro post-proccesing in this setting!

```{r}
out_fl <- fastLink::fastLink(file1, 
                   file2, 
                   varnames = names(file1)[c(2, 3, 5, 6)],
                   stringdist.match = names(file1)[c(2, 3)], 
                   partial.match = names(file1)[c(2, 3)],
                   cut.a = 1, cut.p = .75, dedupe.matches = F, 
                   threshold.match = .5) # comparable threshold

# more false positives than fabl_mm
data.frame(target_id = out_fl$matches$inds.a, 
           base_id = out_fl$matches$inds.b)
```

# Multilink

TBD, comparison with multilink.
```{r}

all_records <- rbind(file1, file2)[, c(2, 3, 5, 6)]
all_records$occup <- as.character(all_records$occup)
cd_multilink <- multilink::create_comparison_data(all_records, 
                                  types = c("lv", "lv", "bi", "bi"), 
                                  breaks = list(c(0, .25, .5), 
                                                c(0, .25, .5), 
                                                NA, 
                                                NA), 
                                  file_sizes = c(n1, n2), 
                                  duplicates = c(1, 1), 
                                  verbose = T)
prior <- multilink::specify_prior(cd_multilink, )

chain_multilink <- multilink::gibbs_sampler(cd_multilink, prior, n_iter = S)
result_ML <- multilink::find_bayes_estimate(chain_multilink$partitions, burn)

result_ML

```

