---
title: "fabl_with_duplicates"
output: html_document
date: "2024-03-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Functions

```{r}
devtools::load_all()
```

## Simulate Comparison Data

With this specification, 20 records in $X_2$ have matches in $X_1$. Of those 20, 10 have two matches. Of those 10, 5 have 3 matches. And of those 5, one has 4 matches. 

```{r}
n1 <- 500# target
n2 <- 500 # base
#overlap <- c(20, 10, 5, 1)
#overlap <- c(1000, 250, 5)
overlap = n2/2
S = 100
burn = S * .1

m <- rep(c(.95, .05), 5)
u <- c(.01, .99, .01, .99,
       1/30, 1- 1/30, 1/12, 1 - 1/12, 1/15, 1 - 1/15)

levels <- rep(2, 5)
#cd <- simulate_comparisons_mm(m, u, levels, n1, n2, overlap)
cd <- simulate_comparisons(m, u, levels, n1, n2, overlap)
Z_true_long <- make_Zhat_pairs(cd$Z_true)
hash <- hash_comparisons(cd, all_patterns = F)

#out <- variational_fastlink(hash)
```


```{r}
out_mm <- fabl_mm(hash, max_K = 1)
result_mm <- estimate_links_mm(out_mm, hash, resolve = F)
evaluate_links(result_mm$Z_hat[, 1:2], Z_true_long, n1, "pairs")


out <- fabl(hash)
result <- estimate_links(out, hash, resolve = F)
Z_hat <- make_Zhat_pairs(result$Z_hat)
evaluate_links(Z_hat, Z_true_long, n1, "pairs")
```


```{r}
out_fl <- variational_fastlink(hash)
estimate_fl <- estimate_links_fl(out_fl, hash)
Z_hat <- data.frame(id_1 = estimate_fl$fs_linkages$a,
                    id_2 = estimate_fl$fs_linkages$b)

evaluate_links(Z_hat, cd$Z_true_long, n1, "pairs")
#estimate_fl$fs_linkages[, c(1, 2, 5)]
#evaluate_links(Z_hat, Ztrue_pairs, n1, "pairs")
```

# Comparison

When we know that only one file has duplicates, both approaches are decent options. We could do experiments to test which approach is more accuate, if there is any difference at all.

However, the first approach is amenable to `vabl`, which is probably more desireable in practice. 

In the other document, I look at how the multiple match approach can be used in situations where both files have duplications. 
